On Adding Pattern Matching to Haskell-based Deeply Embedded Domain Specific Languages

### 2020-10-08 paper/paper.tex
Fix rewrite rule figure a bit
Removed some references to the C backend and Church encoding sections that were removed

\begin{itemize}
  \item A representation of pattern matching in a Haskell EDSL (Section~\ref{sec:PatRep})
  \item A representation of lambdas (Section~\ref{sec:LamRep}) in the EDSL, taking advantage of
  the fact that both pattern matching and tail recursion are already captured in
  the EDSL.
\item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section~\ref{sec:CorePlugin})
\item An implementation of a interpreter for the "standard" semantics of the EDSL (Section~\ref{sec:StdSemantics}).
\item An outline of a C backend for this EDSL (Section~\ref{sec:CBackend}).
\end{itemize}

In this paper, a C backend is given as an example in Section \ref{sec:CBackend}. The Core plugin will
translate a subset of Haskell to the EDSL we have specified. The C backend will
then take expressions written in this EDSL and translate them to C code. This C
code can be compiled by a standard C compiler. In effect, the subset of Haskell
represented in the EDSL is compiled to C.

@@

A C backend is described in Section \ref{sec:CBackend}. However, other backends
could be constructed, targeting different architectures.

@@

The process of transforming a tail recursive function in the DSL to a 
representation which could be passed into the C backend and used
to generate a traditional iterative loop goes as follows.

@@

@@

\begin{wrapfigure}{R}{0.5\linewidth}
  % \centering
  \resizebox{0.5\columnwidth}{7cm}{\includegraphics{Diagrams/Flowchart.pdf}}
  % \includegraphics{Diagrams/Flowchart.pdf}
   \caption{Control Flow of the Core Plugin}
   \label{fig:CorePlugin}
\end{wrapfigure}%

@@

  \begin{wrapfigure}{R}{0.6\linewidth}

@@

\resizebox{0.9\linewidth}{!}{

@@

In this paper:
\begin{itemize}
  \item We address the goal of translating Haskell pattern matching into an
    EDSL. An example usage of this mechanism is given in Section
    \ref{sec:CBackend} in the form of a transformation of a subset of Haskell
    into an EDSL that is then used to generate C code, effectively compiling
    that subset of Haskell into C.

  \item A representation of pattern matching via a deep embedding of Church
    encodings of products and coproducts presented in Section \ref{sec:Church}.
    This encoding relies on having a uniform representation of algebraic data
    types.

>>>>

\begin{itemize}
  \item A representation of pattern matching in a Haskell EDSL (Section~\ref{sec:PatRep})
  \item A representation of lambdas (Section~\ref{sec:LamRep}) in the EDSL, taking advantage of
  the fact that both pattern matching and tail recursion are already captured in
  the EDSL.
\item A GHC Core plugin which transforms a subset of standard Haskell code
  into this EDSL for pattern matching, extended with tail recursion,
  lambdas and primitive operations (Section~\ref{sec:CorePlugin})
\item An implementation of a interpreter for the "standard" semantics of the EDSL (Section~\ref{sec:StdSemantics}).
% \item An outline of a C backend for this EDSL (Section~\ref{sec:CBackend}).
\end{itemize}

% In this paper, a C backend is given as an example in Section \ref{sec:CBackend}. The Core plugin will
% translate a subset of Haskell to the EDSL we have specified. The C backend will
% then take expressions written in this EDSL and translate them to C code. This C
% code can be compiled by a standard C compiler. In effect, the subset of Haskell
% represented in the EDSL is compiled to C.

@@

% A C backend is described in Section \ref{sec:CBackend}. However, other backends
% could be constructed, targeting different architectures.

@@

The process of transforming a tail recursive function in the DSL to a 
representation which could be passed into a backend and used
to generate a traditional iterative loop goes as follows.

@@

\begin{wrapfigure}{r}{0.5\linewidth}
  % \centering
  \resizebox{0.5\columnwidth}{7cm}{\includegraphics{Diagrams/Flowchart.pdf}}
  % \includegraphics{Diagrams/Flowchart.pdf}
   \caption{Control Flow of the Core Plugin}
   \label{fig:CorePlugin}
\end{wrapfigure}%

@@

@@

  \begin{wrapfigure}{r}{0.6\linewidth}

@@

\resizebox{1\linewidth}{!}{

@@

In this paper:
\begin{itemize}
  \item We address the goal of translating Haskell pattern matching into an
    EDSL.

    % An example usage of this mechanism is given in Section
    % \ref{sec:CBackend} in the form of a transformation of a subset of Haskell
    % into an EDSL that is then used to generate C code, effectively compiling
    % that subset of Haskell into C.

  % \item A representation of pattern matching via a deep embedding of Church
  %   encodings of products and coproducts presented in Section \ref{sec:Church}.
  %   This encoding relies on having a uniform representation of algebraic data
  %   types.
